---
title: "Author Metrics"
author: "AMIT"
date: "April 17, 2020"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Degree

df= read.csv("C:/Users/amitd/Desktop/FA/MasterDegree.csv")
dflth = subset(df,df$LowToHigh=="LTH")
dfhtl = subset(df,df$HighToLow=="HTL")
dfclp = subset(df,df$ConsistentlyLowPerf=="CLP")
dfchp = subset(df,df$ConsistentlyHighPerf =="CHP")



dfchp[,4:24]
M <- as.matrix(dfchp[,4:24])
M
x <- c(1997,1998,1999,2000,2001,2002,2003,2004,2005,2006,2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017)
length(x)
dim(M)

```{r echo=FALSE}

plot(x, seq(from=0, to = 100, length.out = length(x)), type = "n",xlab = "Years", ylab = "Degree")

lines(x, M[1, ], col = rgb(1,0,0,alpha = 1))
lines(x, M[2, ], col = rgb(1,0,1,alpha = 1))
lines(x, M[3, ], col = rgb(0.4,0.5,0.5,alpha = 1))
lines(x, M[4, ], col = rgb(0.5,0,0,alpha = 1))
```

dfclp[,4:24]
M <- as.matrix(dfclp[,4:24])
M
x <- c(1997,1998,1999,2000,2001,2002,2003,2004,2005,2006,2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017)
length(x)
dim(M)
```{r echo=FALSE}

plot(x, seq(from=0, to = 100, length.out = length(x)), type = "n",xlab = "Years", ylab = "Degree")

lines(x, M[1, ], col = rgb(1,0,0,alpha = 1))
lines(x, M[2, ], col = rgb(1,0,1,alpha = 1))
lines(x, M[3, ], col = rgb(0.4,0.5,0.5,alpha = 1))
lines(x, M[4, ], col = rgb(0.5,0,0,alpha = 1))
```

dfhtl[,4:24]
M <- as.matrix(dfhtl[,4:24])
M
x <- c(1997,1998,1999,2000,2001,2002,2003,2004,2005,2006,2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017)
length(x)
dim(M)
```{r echo=FALSE}

plot(x, seq(from=0, to = 65, length.out = length(x)), type = "n",xlab = "Years", ylab = "Degree")

lines(x, M[6, ], col = rgb(1,0,0,alpha = 1))
lines(x, M[3, ], col = rgb(1,0,1,alpha = 1))
lines(x, M[4, ], col = rgb(0.4,0.5,0.5,alpha = 1))
lines(x, M[5, ], col = rgb(0.5,0,0,alpha = 1))
```



dflth[,4:24]
M <- as.matrix(dflth[,4:24])
M
x <- c(1997,1998,1999,2000,2001,2002,2003,2004,2005,2006,2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017)
length(x)
dim(M)
```{r echo=FALSE}

plot(x, seq(from=0, to = 200, length.out = length(x)), type = "n",xlab = "Years", ylab = "Degree")

lines(x, M[2, ], col = rgb(1,0,0,alpha = 1))
lines(x, M[3, ], col = rgb(1,0,1,alpha = 1))
lines(x, M[4, ], col = rgb(0.4,0.5,0.5,alpha = 1))
lines(x, M[5, ], col = rgb(0.5,0,0,alpha = 1))
```


##Betweenness

dfbt= read.csv("C:/Users/amitd/Desktop/FA/MasterBetweenness.csv")
dflthbt = subset(dfbt,dfbt$LowToHigh=="LTH")
dfhtlbt = subset(dfbt,dfbt$HighToLow=="HTL")
dfclpbt = subset(dfbt,dfbt$ConsistentlyLowPerf=="CLP")
dfchpbt = subset(dfbt,dfbt$ConsistentlyHighPerf =="CHP")

dfchpbt[,4:24]
M <- as.matrix(dfchpbt[,4:24])
M
x <- c(1997,1998,1999,2000,2001,2002,2003,2004,2005,2006,2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017)
length(x)
dim(M)

```{r echo=FALSE}

plot(x, seq(from=0, to = 1000000, length.out = length(x)), type = "n",xlab = "Years", ylab = "Betweenness")

lines(x, M[1, ], col = rgb(1,0,0,alpha = 1))
lines(x, M[2, ], col = rgb(1,0,1,alpha = 1))
lines(x, M[3, ], col = rgb(0.4,0.5,0.5,alpha = 1))
lines(x, M[4, ], col = rgb(0.5,0,0,alpha = 1))
```


dfclpbt[,4:24]
M <- as.matrix(dfclpbt[,4:24])
M
x <- c(1997,1998,1999,2000,2001,2002,2003,2004,2005,2006,2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017)
length(x)
dim(M)
```{r echo=FALSE}

plot(x, seq(from=0, to = 1000000, length.out = length(x)), type = "n",xlab = "Years", ylab = "Betweenness")

lines(x, M[9, ], col = rgb(1,0,0,alpha = 1))
lines(x, M[8, ], col = rgb(1,0,1,alpha = 1))
lines(x, M[6, ], col = rgb(0.4,0.5,0.5,alpha = 1))
lines(x, M[5, ], col = rgb(0.5,0,0,alpha = 1))
```


dfhtlbt[,4:24]
M <- as.matrix(dfhtlbt[,4:24])
M
x <- c(1997,1998,1999,2000,2001,2002,2003,2004,2005,2006,2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017)
length(x)
dim(M)
```{r echo=FALSE}

plot(x, seq(from=0, to = 1000000, length.out = length(x)), type = "n",xlab = "Years", ylab = "Betweenness")

lines(x, M[9, ], col = rgb(1,0,0,alpha = 1))
lines(x, M[10, ], col = rgb(1,0,1,alpha = 1))
lines(x, M[11, ], col = rgb(0.4,0.5,0.5,alpha = 1))
lines(x, M[12, ], col = rgb(0.5,0,0,alpha = 1))
```
dflthbt[,4:24]
M <- as.matrix(dflthbt[,4:24])
M
x <- c(1997,1998,1999,2000,2001,2002,2003,2004,2005,2006,2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017)
length(x)
dim(M)
```{r echo=FALSE}

plot(x, seq(from=0, to = 1000000, length.out = length(x)), type = "n",xlab = "Years", ylab = "Betweenness")

lines(x, M[2, ], col = rgb(1,0,0,alpha = 1))
lines(x, M[3, ], col = rgb(1,0,1,alpha = 1))
lines(x, M[4, ], col = rgb(0.4,0.5,0.5,alpha = 1))
lines(x, M[5, ], col = rgb(0.5,0,0,alpha = 1))
```


##Eigen Value

dfev= read.csv("C:/Users/amitd/Desktop/FA/MasterEigenVector.csv")
dflthev = subset(dfev,dfev$LowToHigh=="LTH")
dfhtlev = subset(dfev,dfev$HighToLow=="HTL")
dfclpev = subset(dfev,dfev$ConsistentlyLowPerf=="CLP")
dfchpev = subset(dfev,dfev$ConsistentlyHighPerf =="CHP")

dfchpev[,4:24]
M <- as.matrix(dfchpev[,4:24])
M
x <- c(1997,1998,1999,2000,2001,2002,2003,2004,2005,2006,2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017)
length(x)
dim(M)


```{r echo=FALSE}

plot(x, seq(from=-20, to = 10, length.out = length(x)), type = "n",xlab = "Years", ylab = "Log Eigen Value")

lines(x, log10(M[1, ]), col = rgb(1,0,0,alpha = 1))
lines(x, log10(M[2, ]), col = rgb(1,0,1,alpha = 1))
lines(x, log10(M[3, ]), col = rgb(0.4,0.5,0.5,alpha = 1))
lines(x, log10(M[4, ]), col = rgb(0.5,0,0,alpha = 1))
```

dfclpev[,4:24]
M <- as.matrix(dfclpev[,4:24])
M
x <- c(1997,1998,1999,2000,2001,2002,2003,2004,2005,2006,2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017)
length(x)
dim(M)

```{r echo=FALSE}

plot(x, seq(from=-20, to = 10, length.out = length(x)), type = "n",xlab = "Years", ylab = "Log Eigen Value")

lines(x, log10(M[9, ]), col = rgb(1,0,0,alpha = 1))
lines(x, log10(M[8, ]), col = rgb(1,0,1,alpha = 1))
lines(x, log10(M[6, ]), col = rgb(0.4,0.5,0.5,alpha = 1))
lines(x, log10(M[5, ]), col = rgb(0.5,0,0,alpha = 1))
```


dfhtlev[,4:24]
M <- as.matrix(dfhtlev[,4:24])
M
x <- c(1997,1998,1999,2000,2001,2002,2003,2004,2005,2006,2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017)
length(x)
dim(M)

```{r echo=FALSE}

plot(x, seq(from=-20, to = 10, length.out = length(x)), type = "n",xlab = "Years", ylab = "Log Eigen Value")

lines(x, log10(M[9, ]), col = rgb(1,0,0,alpha = 1))
lines(x, log10(M[10, ]), col = rgb(1,0,1,alpha = 1))
lines(x, log10(M[11, ]), col = rgb(0.4,0.5,0.5,alpha = 1))
lines(x, log10(M[12, ]), col = rgb(0.5,0,0,alpha = 1))
```

dflthev[,4:24]
M <- as.matrix(dflthev[,4:24])
M
x <- c(1997,1998,1999,2000,2001,2002,2003,2004,2005,2006,2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017)
length(x)
dim(M)


```{r echo=FALSE}

plot(x, seq(from=-20, to = 10, length.out = length(x)), type = "n",xlab = "Years", ylab = "Log Eigen Value")

lines(x, log10(M[2, ]), col = rgb(1,0,0,alpha = 1))
lines(x, log10(M[3, ]), col = rgb(1,0,1,alpha = 1))
lines(x, log10(M[4, ]), col = rgb(0.4,0.5,0.5,alpha = 1))
lines(x, log10(M[5, ]), col = rgb(0.5,0,0,alpha = 1))
```

##Closeness

dfcl= read.csv("C:/Users/amitd/Desktop/FA/MasterCloseness.csv")
dflthcl = subset(dfcl,dfcl$LowToHigh=="LTH")
dfhtlcl = subset(dfcl,dfcl$HighToLow=="HTL")
dfclpcl = subset(dfcl,dfcl$ConsistentlyLowPerf=="CLP")
dfchpcl = subset(dfcl,dfcl$ConsistentlyHighPerf =="CHP")

dfchpcl[,4:24]
M <- as.matrix(dfchpcl[,4:24])
M
x <- c(1997,1998,1999,2000,2001,2002,2003,2004,2005,2006,2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017)
length(x)
dim(M)
```{r echo=FALSE}

plot(x, seq(from=0, to = 0.0005, length.out = length(x)), type = "n",xlab = "Years", ylab = "Closeness")

lines(x, M[2, ], col = rgb(1,0,0,alpha = 1))
lines(x, M[3, ], col = rgb(1,0,1,alpha = 1))
lines(x, M[4, ], col = rgb(0.4,0.5,0.5,alpha = 1))
lines(x, M[1, ], col = rgb(0.5,0,0,alpha = 1))
```

dfclpcl[,4:24]
M <- as.matrix(dfclpcl[,4:24])
M
x <- c(1997,1998,1999,2000,2001,2002,2003,2004,2005,2006,2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017)
length(x)
dim(M)
```{r echo=FALSE}

plot(x, seq(from=0, to = 0.0005, length.out = length(x)), type = "n",xlab = "Years", ylab = "Closeness")

lines(x, jitter(M[9, ]), col = rgb(1,0,0,alpha = 1))
lines(x, jitter(M[8, ]), col = rgb(1,0,1,alpha = 1))
lines(x, jitter(M[6, ]), col = rgb(0.4,0.5,0.5,alpha = 1))
lines(x, jitter(M[5, ]), col = rgb(0.5,0,0,alpha = 1))
```


dfhtlcl[,4:24]
M <- as.matrix(dfhtlcl[,4:24])
M
x <- c(1997,1998,1999,2000,2001,2002,2003,2004,2005,2006,2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017)
length(x)
dim(M)
```{r echo=FALSE}

plot(x, seq(from=0, to = 0.0005, length.out = length(x)), type = "n",xlab = "Years", ylab = "Closeness")

lines(x, M[9, ], col = rgb(1,0,0,alpha = 1))
lines(x, M[10, ], col = rgb(1,0,1,alpha = 1))
lines(x, M[11, ], col = rgb(0.4,0.5,0.5,alpha = 1))
lines(x, M[12, ], col = rgb(0.5,0,0,alpha = 1))
```


dflthcl[,4:24]
M <- as.matrix(dflthcl[,4:24])
M
x <- c(1997,1998,1999,2000,2001,2002,2003,2004,2005,2006,2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017)
length(x)
dim(M)
```{r echo=FALSE}

plot(x, seq(from=0, to = 0.0005, length.out = length(x)), type = "n",xlab = "Years", ylab = "Closeness")

lines(x, M[2, ], col = rgb(1,0,0,alpha = 1))
lines(x, M[3, ], col = rgb(1,0,1,alpha = 1))
lines(x, M[4, ], col = rgb(0.4,0.5,0.5,alpha = 1))
lines(x, M[5, ], col = rgb(0.5,0,0,alpha = 1))
```

